Multispecies survey specifications

### 2020-11-05 msSurveysTest.Rmd
all new plots and add to index

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(here)
library(tidyverse)  
library(atlantisom)
library(ggthemes)

@@

# census length comps each survey
lf_census_prop <- list()
for(s in names(len_comp_data)){
  lcomp <- as.data.frame(len_comp_data[[s]][[1]])
  lf_census_tot <- aggregate(lcomp$atoutput,list(lcomp$species, lcomp$time),sum )
  names(lf_census_tot) <- c("species", "time","totlen")
  lf_census <- left_join(lcomp, lf_census_tot) %>%
    rename(censuslen = atoutput)
  lf_census_prop[[s]] <- lf_census
}

@@

@@

    ggplot(mapping=aes(x=upper.bins)) +
    {if(!is.null(truedat)) geom_bar(data=truedat, aes(weight = censuslen/totlen), fill="Census Len Comp", alpha = 5/10)} +
    geom_bar(data=dat, aes(weight = atoutput/effN), fill="Len Comp") +
    theme_tufte() +
    xlab("length (cm)") +
    {if(is.null(truedat)) ylab("number")} +
    {if(!is.null(truedat)) ylab("proportion")} +
    labs(subtitle = paste(scenario.name,
                          dat$species)) +
    facet_wrap(~time, ncol=6, scales="free_y")

@@

for(s in names(len_comp_data)){
  cat("  \n##### ",  s,"  \n")
  lcompsub <- as.data.frame(len_comp_data[[s]][[1]]) %>% filter(time %in% c(150:270)) %>%
    group_by(species) %>%
    left_join(., lf_census_prop[[s]]) %>%
    #group_map(~ plotlen(.x), keep = TRUE)
    group_map(~ plotlen(.x, effN = 10000, truedat = 1), keep = TRUE) # plots merged true length comp

@@

@@

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)
library(here)
library(tidyverse)  
library(atlantisom)
library(ggthemes)

@@

# census length comps each survey
lf_census_prop <- list()
for(s in names(len_comp_data)){
  lcomp <- as.data.frame(len_comp_data[[s]][[1]])
  lf_census_tot <- aggregate(lcomp$atoutput,list(lcomp$species, lcomp$time),sum )
  names(lf_census_tot) <- c("species", "time","totlen")
  lf_census <- left_join(lcomp, lf_census_tot) %>%
    rename(censuslen = atoutput)
  lf_census_prop[[s]] <- lf_census
}
#lf_census_prop <- bind_rows(lf_census_prop) flatten, only works if surveys at different times

@@

# note on ggplot default colors, can get the first and second using this
# library(scales)
# show_col(hue_pal()(2))

@@

  cols <- c("Census Lcomp"="#00BFC4","Sample Lcomp"="#F8766D")  
  ggplot(mapping=aes(x=upper.bins)) +
    {if(is.null(truedat)) geom_bar(data=dat, aes(weight = atoutput/effN))} +
    {if(!is.null(truedat)) geom_bar(data=dat, aes(weight = censuslen/totlen, fill="Census Lcomp"), alpha = 5/10)} +
    {if(!is.null(truedat)) geom_bar(data=dat, aes(weight = atoutput/effN, fill="Sample Lcomp"), alpha = 5/10)} +
    theme_tufte() +
    theme(legend.position = "bottom") +
    xlab("length (cm)") +
    {if(is.null(truedat)) ylab("number")} +
    {if(!is.null(truedat)) ylab("proportion")} +
    scale_colour_manual(name="", values=cols) +
    labs(subtitle = paste(scenario.name,
                          dat$species)) +
    facet_wrap(~time, ncol=6, scales="free_y")

@@

#### Survey length composition
```{r, results="asis", message=FALSE}

for(s in names(len_comp_data)){
  cat("  \n##### ",  s,"  \n")
  lcompsub <- as.data.frame(len_comp_data[[s]][[1]]) %>% filter(time %in% c(150:270)) %>%
    group_by(species) %>%
    left_join(., lf_census_prop[[which(names(len_comp_data) == s)]]) %>%
    #group_map(~ plotlen(.x), keep = TRUE)
    group_map(~ plotlen(.x, effN = 10000, truedat = 1), keep = TRUE) # plots merged true length comp

@@

for(s in names(age_comp_data)){
  cat("  \n##### ",  s,"  \n")
  acompsub <- as.data.frame(age_comp_data[[s]][[1]]) %>% filter(time %in% c(150:270)) %>%
    group_by(species) %>%
    left_join(., trueNagecl) %>%
    #group_map(~ Natageplot(.x), keep = TRUE) # plots only sampled age comp
    group_map(~ Natageplot(.x, effN = 10000, truedat = 1), keep = TRUE) # plots merged true age comp

@@

for(s in names(annage_comp_data)){
  cat("  \n##### ",  s,"  \n")
  acompsub <- as.data.frame(annage_comp_data[[s]][[1]]) %>% filter(time %in% c(150:270)) %>%
    group_by(species) %>%
    left_join(., trueNage) %>%
    #group_map(~ Natageplot(.x), keep = TRUE) # plots only sampled age comp
    group_map(~ Natageplot(.x, effN = 10000, truedat = 1), keep = TRUE) # plots merged true age comp
